Drawing Math

### 2022-05-08 paper/Paper.tex
prog

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}

@@

\subsubsection{Digital sum}
Next, we introduce the idea digitial sums.
For some number $N \in \N$, $N$ can be represented in base $b$ via
\begin{equation}
  N = \sum_{i=0}^{m} d_i b^i
\end{equation}
where $m = \lceil \log_b N \rceil$ and, $\forall i \in [m]$, $d_i \in \Z_b$.
Then, we define function $\mathrm{digSum}: \N \rightarrow \Z_b$
to give the digital sum such that
\begin{equation}
  \mathrm{digSum}(N) = \sum_{i=0}^{m} d_i.
\end{equation}

Moreover, define function $\mathrm{digSumPeriodic}: \N^4 \rightarrow \Z_b$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriod} \mathrm{digit}(n, d, b, i)
\end{equation}

@@

\subsubsection{Finding a period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
So, after period $\rationalPeriodTotal$,
\begin{align*}
  \theta_{i + \rationalPeriodTotal} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriodTotal + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
  &= \left(\theta_{i} + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic\right) \mod b\\
  &= \theta_{i} \mod b + \frac{\rationalPeriodTotal}{\rationalPeriod} \digSumPeriodic \mod b.
\end{align*}
So, after $p$ periods of length $\rationalPeriodTotal$ where $p \cdot \frac{\rationalPeriodTotal}{\rationalPeriod}  \cdot \digSumPeriodic \equiv 0 \mod b$,
$$
\theta_{i + p\rationalPeriodTotal} = \theta_i.
$$
For simplicity, lets define
$$
  T^j = p\rationalPeriodTotal
$$
where $T^j$ is a period of the state for seed $j$.
% TODO: remove $i$ from the state and somehow have it be implicit....

@@

\subsubsection{Closing along a single dimension}
Finally, to see if a shape will close,
we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
First, let $A_d = \set{j \mid j \in [k] \and \inclIndic{d}{j} = 1}$
We can then see that
\begin{align*}
&\sum_{i = 1}^T \combSingleTerm{d}\\
&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
\end{align*}

@@

We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$
\begin{align*}
  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \\
  &= \sum_{p = 0}^{x\periodFrac - 1} \sum_{q=0}^{\rationalPeriod - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + b)
    + \sum_{p = 0}  \\
    % ARGS::....
  &= x\cdot \periodFracRational \cdot \digSumPeriodic + .
\end{align*}

Then, 
\begin{align*}
 &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
 =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
\end{align*}

>>>>

%% Custom Commands
\newcommand{\rationalPeriod}{{T^j}'}
\newcommand{\rationalPeriodTotal}{{T}'}
\newcommand{\statePeriod}{T^j}
\newcommand{\seedAngleJ}[2]{{\theta^{#2}_{#1}}}
\newcommand{\seedAngle}[1]{{\theta^j_{#1}}}
\newcommand{\seedAngleNotime}{{\theta}^j}
\newcommand{\state}[2]{{s_{#1}}^{#2}}
\newcommand{\stateNotime}[1]{s^{#1}}
\newcommand{\totalPeriod}{T}
\newcommand{\totalState}{\pmb{s}_i}
\newcommand{\totalStateNotime}{\pmb{s}}
\newcommand{\comb}{Comb}
\newcommand{\combWithState}[1]{Comb\left(s^1_{#1}, s^2_{#1}, ..., s^k_{#1}\right)}
\newcommand{\inclIndic}[2]{{\mathrm{incl}_{#1}^{#2}}}
\newcommand{\combSingleTerm}[1]{\prod_{j=1}^k \cos(\theta_j) ^ {\inclIndic{#1}{j}}}
\newcommand{\digSumPeriodic}{\mathrm{digSumPeriodic}^j}

@@

\subsubsection{Digital sum}
Next, we introduce the idea digital sums.
For some number $N \in \N$, $N$ can be represented in base $b$ via
\begin{equation}
  N = \sum_{i=0}^{m} d_i b^i
\end{equation}
where $m = \lceil \log_b N \rceil$ and, $\forall i \in [m]$, $d_i \in \Z_b$.
Then, we define function $\mathrm{digSum}: \N \rightarrow \Z_b$
to give the digital sum such that
\begin{equation}
  \mathrm{digSum}(N) = \sum_{i=0}^{m} d_i.
\end{equation}

Moreover, define function $\digSumPeriodic \in \Z_b$
such that
% TODO: define T within the func from another func
% TODO: bettr defn
\begin{equation}
  \digSumPeriodic = \sum_{i = i_0}^{i_0 + \rationalPeriodTotal} \mathrm{digit}(n, d, b, i)
\end{equation}

@@

\subsubsection{Finding a period of $\seedAngleNotime$} % TODO: redifine things in terms of theta...
For $(n^j, b^j, d^j, \theta_i^j) = s_i^j$,
recall that $\seedAngle{i + 1} = \seedAngle{i} + \mathrm{digit}(n, b, d, i) \mod b$.
So, after period $\rationalPeriodTotal$,
\begin{align*}
  \theta_{i + \rationalPeriodTotal} &= \left(\theta_{i} + \sum_{\ell = i}^{\rationalPeriodTotal + i} \mathrm{digit}(n, b, d, \ell)\right) \mod b\\
  &= \left(\theta_{i} +  \digSumPeriodic\right) \mod b\\
  &= \theta_{i} \mod b +  \digSumPeriodic \mod b.
\end{align*}
So, after $p$ periods of length $\rationalPeriodTotal$ where $p  \cdot \digSumPeriodic \equiv 0 \mod b$,
$$
\theta_{i + p\rationalPeriodTotal} = \theta_i.
$$
For simplicity, lets define
$$
  T^j = p\rationalPeriodTotal
$$
where $T^j$ is a period of the state for seed $j$.
% TODO: remove $i$ from the state and somehow have it be implicit....

@@

\subsubsection{Closing along a single dimension}
Finally, to see if a shape will close,
we just need to find if equation \eqref{eq:singleDelta0} holds true for all dimensions.
First, let $A_d = \set{j \mid j \in [k] \; ; \inclIndic{d}{j} = 1}$
We can then see that
\begin{align*}
&\sum_{i = 1}^T \combSingleTerm{d}\\
&=\sum_{i = 1}^T \prod_{j = 1}^k \left(\half \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\right)^\inclIndic{d}{j}\\
&=2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
\end{align*}

@@

We can then see that for $(n, b, d, \theta_i) \in \pmb{s}_i$ and $x, y \in \N$ where $y < \rationalPeriodTotal$,
\begin{align}
  \seedAngle{x \rationalPeriodTotal + y} &= \sum_{i = 0}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, i) \notag \\
  &= \sum_{p = 0}^{(x- 1)\rationalPeriodTotal} \sum_{q=0}^{\rationalPeriodTotal - 1} \mathrm{digit}(n, b, d, p\rationalPeriodTotal + q)
    + \sum_{p = x \rationalPeriodTotal}^{x \rationalPeriodTotal + y} \mathrm{digit}(n, b, d, p) \notag \\
    % ARGS::....
  \label{eq:angleBreakdown}
  &= x \cdot \digSumPeriodic + \sum_{p = x \rationalPeriodTotal}^{\rationalPeriodTotal + y}\mathrm{digit}(n, b, d, p) \notag \\
  &= x \cdot \digSumPeriodic + \sum_{p = 0}^{y}\mathrm{digit}(n, b, d, p)
\end{align}
because $\mathrm{digit}(n, b, d, x\rationalPeriodTotal + \ell) = \mathrm{digit}(n, b, d, \ell)$ for any $\ell \in \N$
by definition of periodicity.

Observe that 
\begin{align*}
 &\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right) \\
 =& \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} + \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) 
  + \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} + ... + \seedAngleJ{p \rationalPeriodTotal + q}{d}) + ... \\
  &+ \exp(\seedAngleJ{p \rationalPeriodTotal + q}{1} - \seedAngleJ{p \rationalPeriodTotal + q}{2} - ... - \seedAngleJ{p \rationalPeriodTotal + q}{d})
\end{align*}
which then equals
\begin{equation}
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right).
\end{equation}

Then, 
\begin{align*}
 &2^{-|A|} \sum_{i = 1}^T \prod_{j \in A_d} \left(e^{\seedAngle{i} I} +  e^{-\seedAngle{i} I}\right)\\
 =& 2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}\prod_{j \in A_d} \left(e^{\seedAngle{p \rationalPeriodTotal + q} I} +  e^{-\seedAngle{p \rationalPeriodTotal + q} I}\right)\\
 =&
  2^{-|A|} \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right)\\
 =&
  2^{-|A|} 
 \sum_{\beta \in \set{0,1}^{|A_d|}} 
     \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right).
\end{align*}

Then, lets fix some $\beta \in \set{0, 1}^{|A_d|}$, we will now show that 
\begin{equation}
\label{eq:wts01}  
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \seedAngle{p \rationalPeriodTotal + q}I
      \right)
\end{equation}
always equals $0$ or $1$ for any choice of $\beta$.

Observe that 
\begin{align}
  \exp(\seedAngle{p \rationalPeriodTotal + q}I) &= \exp\left(p \cdot \digSumPeriodic +
    \sum_{\ell = p \rationalPeriodTotal}^{p \rationalPeriodTotal + q}\mathrm{digit}(n, b, d, \ell)\right) \tag{by equation \eqref{eq:angleBreakdown}} \\
    \label{eq:expBreakdown}
    &= \exp\left(p \cdot \digSumPeriodic\right) \exp\left(\sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)\right).
\end{align}

So then, by equation \eqref{eq:expBreakdown}, we get that
\begin{align}
&\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
    \seedAngle{p \rationalPeriodTotal + q}I = 
\right)\notag \\ 
\label{eq:decomposeExp}
=&
\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
    \cdot p \cdot
    \digSumPeriodic
\right)
\exp\left(
    \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
\right).
\end{align}

We then use \eqref{eq:decomposeExp} to show that \eqref{eq:wts01} equals
\begin{equation*}
  \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \left[
    \exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)
  \left(
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
    \exp\left(
        \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
          \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell).
    \right)\right)\right].
\end{equation*}
% TODO: second part can be thought of as a constant for now... ie C2=
% Then, we can think of the inner first sum as a constant of sorts, (C1)
% And we know that pI(T/T') = 1 and that pI0 = 1. So, if C1 \neq 0, we get some roots of unity
% and then the whole sum is 0...
% If it does equal 0, you have to check if C2 = 0... don't really know how to do this...
% If C1 = 0 and C2 not equal to 0, then

% TODO: then think of notation for the "distributed" polynomial, then you can expand...
% / assignment of +- strings... oy vey

% TODO: no clue what is going on with C2... (maybe throw in some pictures...)

% TODO: overall goal, show this is in coNP...
